[{"problemId": 0, "seed": 0, "tag": "", "solution": "ia! ia!lei!lei!aia! ia!lei!llacthulhu fhtagn!akyuggothr'lyehei!paplanet 10r'lyehr'lyehkblue hadesyuggothldcthulhu fhtagn!ppakthe laundryr'lyehr'lyehktsathogguadddlkplanet 10r'lyehei!ldblue hadeslllkyogsothothei!dpkia! ia!aei!kkathe laundryr'lyehkadyogsothothpddlkplanet 10kkyoyodyneadei!ayuggothei!akplanet 10dlakr'lyehyogsothothkkktsathogguabkr'lyehei!ppaakr'lyehr'lyehr'lyehlkkblue hadeskei!dlkblue hadesldei!ppr'lyehpakr'lyehppppdpdalkpkyoyodynealkei!dplanet 10kkkblue hadesllkbkyuggothadr'lyehbr'lyehkei!kyuggothkkppkkyuggothaadia! ia!alaaei!ppadyuggothakei!dddnecronomiconkia! ia!lei!laapthe laundryr'lyehlkyogsothothr'lyehdakthe laundrybyuggothdia! ia!r'lyehlkei!tsathogguaei!lkbcthulhu fhtagn!kplanet 10ppplanet 10adblue hadesei!pr'lyehkthe laundrylbblkblue hadesei!dlakia! ia!r'lyehei!kkkblue hadeskia! ia!pddyogsothothei!klkei!tsathogguadei!ktsathogguaei!pakkyuggothei!pr'lyehkdblue hadeslakr'lyehtsathogguapddei!pddnecronomiconbkkyuggothr'lyehr'lyehkblue hadeslr'lyehdaddtsathogguapaddathe laundrydpr'lyehlkktsathogguaadei!r'lyehptsathogguaktsathogguar'lyehpppddyogsothothr'lyehkei!kplanet 10pmonkeyboyadthe laundryr'lyehpakr'lyehr'lyehbr'lyehlkia! ia!lei!laaia! ia!r'lyehkkayuggothr'lyehpaablue hadesyuggothlkplanet 10pplanet 10ddyogsothothdr'lyehkia! ia!kbyuggothkia! ia!lei!llbaia! ia!kyuggothbkkyogsothothr'lyehkei!kblue hadeslplanet 10ddplanet 10pamonkeyboydtsathogguaei!pakplanet 10the laundrydtsathogguar'lyehadtsathogguaei!ppaktsathogguaklkkkyuggothr'lyehei!pkblue hadeslllkyuggothr'lyehr'lyehlbkyogsothothei!dlkplanet 10r'lyehr'lyehdplanet 10r'lyehei!ldblue hadeslkkplanet 10r'lyehadia! ia!lbddtsathogguappaei!ddr'lyehtsathogguakei!ddnecronomiconkplanet 10r'lyehr'lyehdplanet 10r'lyehpadthe laundryei!lkatsathogguabkld"}]
